
\documentclass[]{svmono}

\usepackage{fancybox}
\usepackage{graphicx}
\usepackage{pdfpages}
\usepackage{color}
\usepackage{epstopdf}
\usepackage[margin=1in, vmargin=1in]{geometry}
\usepackage{amsmath}
\usepackage{float}
\usepackage{listings}
\usepackage{verbatim}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{longtable}
\usepackage{amsmath}
\usepackage{caption}

\usepackage{subcaption}


\usepackage{enumerate}

\usepackage{bashful}

\usepackage{multicol}


\usepackage{textcomp}
\usepackage{hyperref}
%\usepackage[hyphenbreaks]{breakurl}
%\usepackage[hyphens]{url}


\sloppy
\definecolor{lightgray}{gray}{0.5}
\setlength{\parindent}{20pt}


\definecolor{mygreen}{rgb}{0,0.6,0}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.58,0,0.82}

\lstset{ %
  backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
  basicstyle=\footnotesize,        % the size of the fonts that are used for the code
  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
  breaklines=true,                 % sets automatic line breaking
  captionpos=b,                    % sets the caption-position to bottom
  commentstyle=\color{mygreen},    % comment style
  deletekeywords={...},            % if you want to delete keywords from the given language
  escapeinside={\%*}{*)},          % if you want to add LaTeX within your code
  extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
  frame=single,                    % adds a frame around the code
  keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
  keywordstyle=\color{blue},       % keyword style
  language=Python,                 % the language of the code
  morekeywords={*,...},            % if you want to add more keywords to the set
  numbers=left,                    % where to put the line-numbers; possible values are (none, left, right)
  numbersep=5pt,                   % how far the line-numbers are from the code
  numberstyle=\tiny\color{mygray}, % the style that is used for the line-numbers
  rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
  showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
  showstringspaces=false,          % underline spaces within strings only
  showtabs=false,                  % show tabs within strings adding particular underscores
  stepnumber=2,                    % the step between two line-numbers. If it's 1, each line will be numbered
  stringstyle=\color{mymauve},     % string literal style
  tabsize=2,                       % sets default tabsize to 2 spaces
  title=\lstname                   % show the filename of files included with \lstinputlisting; also try caption instead of title
}



\setlength{\parindent}{10pt}


\begin{document}




\begin{titlepage}    
\begin{center}
\vspace*{0in}
\huge{\sc  Old Dominion Univeristy\\  }



\vspace{1in}
\Large{\sc CS 495: Introduction to Web Science \\ Instructor: Michael L. Nelson, Ph.D \\ Fall 2014 4:20pm - 7:10pm R, ECSB 2120\\}

\vspace{1in}
\Large{Assignment \# 8\\}

\vspace{.5cm}
\Large{ \sc George C.  Micros  UIN: 00757376\\ }



\vspace {7cm}

{\large \bf {Honor Pledge}}\\
{I pledge to support the Honor System of Old Dominion University. I will refrain from any form of academic dishonesty or deception, such as cheating or plagIiarism. I am aware that as a member of the academic community it is my responsibility to turn in all suspected violations of the Honor Code. I will report to a hearing if summoned. }\\
\vspace {.5cm}

{Signed \_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_\_}


\today
\end{center}
\end{titlepage}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\author{George C. Micros}
\title{Written Assignment 8}
\subtitle{Fall 2014 \newline  CS 495: Introduction to Web Science\newline Dr. Michael Nelson}
\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\tableofcontents

\chapter{Written Assignment 8}

\noindent


The goal of this project is to use the basic recommendation principles
we have learned for user-collected data. You will modify the code
given to you which performs movie recommendations from the MovieLense
data sets.The MovieLense data sets were collected by the GroupLens Research
Project at the University of Minnesota during the seven-month period
from September 19th, 1997 through April 22nd, 1998. It is available
for download from \url{http://www.grouplens.org/node/73}

There are three files which we will use:


\begin{itemize}

\item  u.data: 100,000 ratings by 943 users on 1,682 movies. Each
user has rated at least 20 movies. Users and items are numbered
consecutively from 1. The data is randomly ordered. This is a tab
separated list of 

user id | item id | rating | timestamp

The time stamps are unix seconds since 1/1/1970 UTC.

Example:

196	242	3	881250949

186	302	3 	891717742

22	377	1 	878887116

244	51	2 	880606923

166	346	1 	886397596

298	474	4 	884182806

115	265	2	881171488

\item  u.item: Information about the 1,682 movies. This is a tab separated list of

movie id | movie title | release date | video release date | IMDb URL | unknown | Action | Adventure | Animation |Children's | Comedy | Crime | Documentary | Drama | Fantasy | Film-Noir | Horror | Musical | Mystery | Romance | Sci-Fi | Thriller | War | Western |

The last 19 fields are the genres, a 1 indicates the movie is of that genre, a 0 indicates it is not; movies can be in several genres at once. The movie ids are the ones used in the u.data data set.

Example:

161|Top Gun (1986)|01-Jan-1986||http://us.imdb.com/M/title-exact?Top%20Gun%20(1986)|0|1|0|0|0|0|0|0|0|0|0|0|0|0|1|0|0|0|0 
162|On Golden Pond (1981)|01-Jan-1981||http://us.imdb.com/M/title-exact?On%20Golden%20Pond%20(1981)|0|0|0|0|0|0|0|0|1|0|0|0|0|0|0|0|0|0|0 
163|Return of the Pink Panther, The (1974)|01-Jan-1974||http://us.imdb.com/M/title-exact?Return%20of%20the%20Pink%20Panther,%20The%20(1974)|0|0|0|0|0|1|0|0|0|0|0|0|0|0| 0|0|0|0|0

\item   u.user: Demographic information about the users. This is a tab
separated list of:

user id | age | gender | occupation | zip code

The user ids are the ones used in the u.data data set.

Example:

1|24|M|technician|85711 
2|53|F|other|94043 
3|23|M|writer|32067 
4|24|M|technician|43537 
5|33|F|other|15213

\end{itemize}

The code for reading from the u.data and u.item files and creating
recommendations is described in the book Programming Collective
Intelligence (check email for more details). You are to modify
recommendations.py to answer the following questions. Each question your
program answers correctly will award you 1 point.



The data was organized using classes for the movies, users and reviews. This helped organized the data in a way that was similar to the way it was represented in the files.

\begin{lstlisting}[caption={Class definitions for movies, users and reviews}]
class movie:
	def __init__(self, data):
		data = data.strip('\n').split('|')		
		self.id 	= int(data[0])
		self.title 	= data[1].replace(',', '')
		self.data 	= data[2]
		self.vid 	= data[3]
		self.url 	= data[4]
		self.genre 	= data[5:len(data)]
		self.scores	= []
		self.cnt	= 0
		self.avg 	= 0
		self.rvwrs	= []

	def avgr(self):
		if self.cnt > 0:
			self.avg = sum(self.scores)/self.cnt
		else:
			self.avg = 0

class user:
	def __init__(self,data):
		data = data.strip('\n').split('|')
		self.id 	= int(data[0])
		self.age	= int(data[1])
		self.sex	= data[2]
		self.job	= data[3]
		self.zip 	= data[4]
		self.film   = {}
		self.cnt	= 0

class review:
	def __init__(self, data):
		data = data.strip('\n').split('\t')
		self.user 	= int(data[0])
		self.item	= int(data[1])
		self.score	= int(data[2])
		self.time	= int(data[3])
\end{lstlisting}

Data was loaded from its respective files, parced and initialized into a new object that was appened to and list of similar objects.

\begin{lstlisting}[caption={Loading data from files to list of objects}]
f = open("./ml-100k/u.item")
for i in f:
	movies.append(movie(i))

f = open("./ml-100k/u.user")
for i in f:
	users.append(user(i))

f = open("./ml-100k/u.data")	
for i in f:
	reviews.append(review(i))
\end{lstlisting}



\include{q1}
\include{q2}
\include{q3}
\include{q4}
\include{q5}
\include{q6}
\include{q7}
\include{q8}
\include{q9}
\include{q10}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\nocite{*}
\bibliography{sources}
\bibliographystyle{unsrt}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%




\end{document}


