\section{Question 1}

\subsection{The Question}

\begin{flushleft}

Choose a blog or a newsfeed (or something similar as long as it has
an Atom or RSS feed).  It should be on a topic or topics of which you
are qualified to provide classification training data.  In other words,
choose something that you enjoy and are knowledgable of.  Find a feed
with at least 100 entries.

Create between four and eight different categories for the entries
in the feed:

examples: 
\begin{itemize}
\item work, class, family, news, deals

\item liberal, conservative, moderate, libertarian

\item sports, local, financial, national, international, entertainment

\item metal, electronic, ambient, folk, hip-hop, pop

\end{itemize}

Download and process the pages of the feed as per the week 12 
class slides.

\end{flushleft}


\subsection{The Answer}


A blog from blogspot was chosen based on the topic and how well it could be described with categories. The topic selected is soccer. The categories are: Spain, England, World, Americas, Germany, Africa, because these are the main themes that arise in the posts. A script was written that uses cURL to make a request of the atom feed page with an additional query of 100 results. This is saved as an .xml file. The classification was done manually and written in ``class.txt''.


\lstset{
    language=Bash,
    label=code:q1,
    caption={Bash script to retrieve Atom feed from blog}
}
\lstinputlisting{../q1/getFeed.sh}







